\section{Work Experience}

% RENDYR INC. %
\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{\textbf{Embedded Systems Engineer}
		\hfill {{Sep. 2017 --- Apr. 2019}}}
	\smallbreak
	\parbox{\linewidth}{Rendyr, Inc.}
	
	\bigskip
	
	Co-founded Rendyr, a desktop robotics company specializing in laser cutters, and worked as the lead software and electrical engineer.
	
	\bigskip
	\begin{itemize}
		
		\item{Designed a motor controller board in Altium that received commands and files over USB and Bluetooth to control a laser cutter.}\\[-.6em]
		
		\item{Created an API for interfacing with touchscreens, flash memory, and external bluetooth controllers in C.}\\[-.6em]
		
		\item{Implemented simulations for two separate products in Processing. Both were able to run both locally and in a web browser. They simulated the motion of the machine, the path the laser would take, and display the expected result.}\\[-.6em]
		
		\item{Helped to raise nearly \$100,000 in funding through investors and competitions.}
		
	\end{itemize}
	\bigskip
	\bigskip
}

% AUTODRIVE - SCIENCE FAIR. %
\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{\textbf{Computer Vision Intern}
		\hfill {{Aug. 2017 --- May 2018}}}
	\smallbreak
	\parbox{\linewidth}{Virginia Tech AutoDrive}
	
	\bigskip
	
	Part of a 3-person R\&D team that developed a camera system for self driving cars. My role on the team was writing the software for the computer vision algorithm.
	
	\bigskip
	\begin{itemize}
		\item{Developed an algorithm for seeing in low light conditions in C++ using OpenCV which combined multiple image streams into a final high dynamic range image.}\\[-.6em]
		
		\item{Implemented the logic of the algorithm onto an FPGA in Verilog to accelerate the processing speed of the images.}\\[-.6em]
		
		\item{Wrote scripts that automatically configured, calibrated, tested the camera system.}
		
	\end{itemize}
	\bigskip
	\bigskip
}

% SPACE@VT %
\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{\textbf{Electrical / Software Engineering Intern}
		\hfill {{May 2017 --- Aug. 2017}}}
	\smallbreak
	\parbox{\linewidth}{Space@VT}
	
	\bigskip
	
	Part of a 3-person R\&D team that developed a camera system for self driving cars. My role on the team was writing the software for the computer vision algorithm.s
	
	\bigskip
	\begin{itemize}
		\item{Designed circuit boards for showing the practical effects of noise on analog and digital signals for a professor's class}\\[-.6em]
		
		\item{Measured and recorded antenna radiation patterns, graphing them in Python using Matplotlib.}\\[-.6em]
		
		\item{Helped a student design team create a CubeSat by writing a Python interface to their IMU sensor}
		
	\end{itemize}
	\bigskip
	\bigskip
}

% SPACE@VT %
\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{\textbf{Computer Vision Software Engineer}
		\hfill {{Aug. 2014 --- Jun. 2017}}}
	\smallbreak
	\parbox{\linewidth}{FRC Robotics Team 401}
	
	\bigskip
	
	Developed algorithms which allowed robots to autonomously find, retrieve, and shoot game pieces during FRC robotics competitions. 

}